Extracting The Power of Dependent Types

### 2021-07-13 paper.tex
Anonymity + space reduction

The main advantage of our approach is twofold: first, it allows
you to implement all these things --- as well as the embedded programs
themselves --- \emph{side by side in a single language}, simplifying
the development. And secondly, it allows you to reuse the typechecker
and evaluator of the host language, saving you a lot of work.
While we showcase a single example, we applied our approach to several other
languages:
\begin{itemize}
\item Kaleidoscope, a minimalist imperative language used in the
  documentation of LLVM.
\item SaC (Single assignment C), a high-performance array language
  that generates efficient code for various architectures.
\item APL (Array Programming Language), another array language with
  heavily overloaded syntax that pioneered the concept of rank- and
  shape-polymorphic programming.
\end{itemize}
For more details on these examples,
refer to~\citet{DBLP:journals/corr/abs-2105-10819}.
This suggests that you are now empowered to apply the proposed
technique to verify code in any language.

>>>>

The main advantage of our approach is twofold: first, it allows
you to implement all these things --- as well as the embedded programs
themselves --- \emph{side by side in a single language}, simplifying
the development. And secondly, it allows you to reuse the typechecker
and evaluator of the host language, saving you a lot of work.
While we showcase a single example, the approach has been applied
to several other languages: Kaleidoscope, a minimalist imperative language;
Single assignment C, a high-performance array language;
APL (Array Programming Language), another array language with
heavily overloaded syntax.
For more details on these examples,
refer to~\citet{DBLP:journals/corr/abs-2105-10819}.

We believe that the reader is now empowered to apply the proposed
technique to verify code in any language.
